---
output:
  pdf_document: 
    extra_dependencies: ["booktabs", "threeparttable"]
---

# R Markdown template

This is an Markdown template created by DIME Analytics.
It is meant to be a reference to show how text formatting in Markdown is combined with R code to produce R Markdown documents.


# Markdown

##  Headers

# This is a header
## Subheader 1
### Subheader 2
#### Subheader 3

## Paragraphs

This is a line of text.
This is another line in the same paragraph.

New paragraphs are separated by two line breaks.

## Text emphasis

Text in italics goes between *asterisks* or _underscores_.

Text in bold goes between **two asterisks** or __two underscores__.

You can combine asterisks and underscores to **emphasize with italics and bold _at the same time_**.

Strikethrough text ~~uses two tildes~~.

## Lists

Ordered lists:

1. Include a number and a dot before every item
2. Also remember to include a blank line before the beginning of the list
1. The actual number does not matter, the item will have the correct order number

Unordered lists:

* You can use an asterisk
+ Or a plus symbol
- Or a minus symbol

## Links

Include the link text in brackets followed by the URL in parentheses.
Like this:

This is [the WB website](https://www.worldbank.org).

#R Code
```{r, echo = FALSE}
data(mtcars)
summary(mtcars)

summary(mtcars$mpg)

```
```{r, echo = FALSE}
plot(mtcars$wt,
mtcars$mpg,
main = "Plot example"
,
xlab = "Car weight"
,
ylab = "Miles per gallon")

```

# Inline code

+ The number of elements in mtcars is:`r nrow(mtcars) `.
+ The mean of weight is: `r mean(mtcars$wt)`.
+ The standard deviation is: `r sd(mtcars$wt)`.

```{r}
library(fixest)
library(dplyr)

est1 <- feols(mpg ~ wt, data = mtcars)
est2 <- feols(mpg ~ wt + hp, data = mtcars)
etable(est1, est2, style.tex = style.tex("aer"), tex = TRUE)

```

